RationalGRL: A Framework for Argumentation and Goal Modeling

### 2017-11-06 formalframework.tex
MASTERFIX

In Section~\ref{sect:overview}, we have shown through a language definition and informal examples from our case study that it is possible to trace elements of the goal model back to their underlying arguments (\textbf{requirement 2}), and that it is possible to determine the effect of changes in the underlying argumentation on the goal model, and vice versa (\textbf{requirement 3}). A formal rendition of this traceability will be presented in this section, in which we present a logical formalization of RationalGRL. This is done for multiple reasons: (i) Most approaches in formal argumentation (cf. Section~\ref{sect:background:pras}) use formal logic, allowing us to employ existing technique directly in order to compute which arguments are accepted and which are rejected, (ii) we can be more precise about how critical questions are answered, (iii) we can show that RationalGRL models can be translated in to valid GRL models and visa versa in a precise way, and (iv) the formal approach is a basis for automating the framework in terms of tool support.

In Sections \ref{sect:formalframework:grl} and \ref{sect:formalframework:rationalgrl} we formalize a static representation of our framework based on the metamodel Figure~\ref{fig:metamodel}). We first provide a formal specification of a GRL model in Section~\ref{sect:formalframework:grl}, and we extend this with arguments and attack links in the second subsection, hereby obtaining a formal specification of a RationalGRL model. In Section~\ref{sect:formalframework:translation} we then present algorithms in order to translate a GRL model into a RationalGRL model, and vice versa. Finally, in Section~\ref{sect:algorithms} we turn to the dynamics of our framework, developing algorithms for instantiating argument schemes and answering critical questions and thus formally capturing the \textsf{INTRO}, \textsf{REPLACE} and \textsf{DISABLE} operations of which examples were previously given in Section~\ref{sect:overview:examples}.

@@

\begin{definition}[General definitions]
\label{def:set-definitions}
We define the following sets:
\begin{itemize}
\item $IETypes = \{Softgoal, Goal, Task, Resource\}$,
\item $LinkTypes = \{PosContr, NegContr, Dep, Decomp\}$\footnote{Recall that for decomposition links we only distinguish between positive and negative contribution. Extending the formalization model to include more values is straightforward.},
\item $Types = IETypes \cup LinkTypes\cup\{Actor, ActIE, GenArg\}$,
\item $Names$ is a finite set of strings,
\item $DecompTypes = \{AND,OR,XOR\}$.
\end{itemize}
\end{definition}
Next, we define an intentional element.

\begin{definition}[Intentional Element]
\label{def:ie}
An intentional element is a tuple $ie = (id, type, name, decomptype)$, where:
\begin{itemize}
\item $id\in \mathbb{N}$ is a unique identifier for the element,
\item $type\in IETypes$ specifies the type of the element,
\item $name \in Names$ is a string description of the element,
\item $decomptype\in DecompType$ refers to the type of decomposition.\footnote{Note that, like in the metamodel, the decomposition type is defined on the element.}
\end{itemize}
The set of intentional elements is denoted by $IE$.
\end{definition}

@@

\begin{definition}[Actor]
\label{def:actor}
An actor is a tuple $act=(id,type, name)$, where:
\begin{itemize}
\item $id\in\mathbb{N}$ is the identifier of the actor, 
\item $type = Actor$ states that this tuple is an actor.
\item $name\in Names$ is a string description of its name.
\end{itemize}
A set of actors is denoted by $Act$.
\end{definition}
We can now formalize the actor in our example (Figure~\ref{fig:example-small}) as $(0,Actor,\text{Traffic Simulator})$.%, and we can for instance state $act_0.name = \text{Traffic Simulator}$.

@@

Note that Actor-IE relations do not have an $id$: they are themselves not elements of a GRL model but rather indicate relations between elements of a GRL model (i.e., intentional elements and actors). The relation between the \emph{Traffic Simulator} actor ($id = 0$) and the \emph{Car objects} resource ($id=1$), for example, can be formalized as $(0, 1)$.

@@

%We also introduce some simplified notation for the links.

@@

Definition \ref{def:grl-model} only sums up the elements of the model and not the constraints that make a \emph{valid} GRL model, viz.

\begin{definition}[Valid GRL Model]
\label{def:valid-grl-model}
A GRL model $GRL=(IE, Act, R_{ActIE}, Contr, Decomp, Dep)$ (Def.~\ref{def:grl-model}) is a \emph{valid GRL model} iff the following conditions are satisfied:
\begin{enumerate}
\item ids are globally unique across IEs, Beliefs, Links, and Actors, i.e., let $X,Y\in \{IE,Act, Belief, Contr, Decomp, Dep\}$. For all $X_i$ and $Y_j$: if $i=j$ then $X=Y$ and $X_i=Y_j$.
\item Intentional elements of actors exist: $\forall (k, ActIE, i,j)\in R_{ActIE}: act_i \in Act \wedge ie_j \in IE$.
\item An intentional element belongs at most to one actor: $\forall ie_i\in IE: |\{(k,ActIE,j,i)\in R_{ActIE}\}| \le 1$.
\item Links connect intentional elements: $\forall (i,type, j,k)\in Link: \{ie_j,ie_k\}\subseteq IE$.
\end{enumerate}
\end{definition}

Let us briefly verify that our previous formalization of Figure~\ref{fig:example-small} satisfies all the constraints of Definition~\ref{def:valid-grl-model}:
\begin{enumerate}
\item All elements in the formalization have different ids, so this constraint is satisfied.
\item $R_{ActIE}$ contains one element for each IE with id $i$, so this constraint is satisfied as well. Note that, in line with the GRL metamodel, links are not related to actors. 
\item There is one actor ($id=0$) and this is the only actor that appears in $R_{ActIE}$ so this constraint is satisfied.
\item All links connect IEs: the contribution links connect elements with ids 2, 3, and 5, which are all IEs; the decomposition links connect elements with ids 4, 5, and 6, which are all IEs; and the dependency link connects id 1 with 4, which are both IEs.
\end{enumerate}

@@

\begin{definition}[Argument]
\label{def:argument}
An argument $A$ is on of the following tuples:
\begin{itemize}
\item An intentional element (Def.~\ref{def:ie}), 
\item An actor $act$ (Def.~\ref{def:actor}),
\item An Actor-IE relation $r_{ActIE}$ (Def.~\ref{def:act-ie-relation}), 
\item A link $link$ (Def.~\ref{def:link}),
\item A generic argument $ga$ (Def.~\ref{def:generic-argument}).
\end{itemize}
\end{definition}

@@

\begin{definition}[Attack Link]
\label{def:link:attack}
Given a set of arguments $Arg$, an attack link is a relation such that $att=(A_i,A_j)$ means:
\begin{itemize}
\item $A_i\in Arg$ is the argument performing that attack,
\item $A_j\in Arg$ is the argument being attacked.
\end{itemize}
The set of attack links is denoted by $Att$.
\end{definition}

As an example, take the arguments $A_5$ for the goal (Generate traffic, $AND$), $A'_5$ for the goal (Generate traffic, $XOR$), $A_4$ for the softgoal (Easy to use) and the generic argument $A_{13}$ (Redundant) against the softgoal (Easy to use). Given these arguments there are two attack links (Figure~\ref{fig:example-small3}), namely $(A'_{5},A_{5})$ and $(A_{13}, A_{4})$.

We now define RationalGRL models.

@@

\begin{flalign*}
A_0 = &(0, Actor, \text{Traffic simulator})&\\
A_1 = &(1, Task, \text{Car objects}, AND),&\\
A_2 = &(2, Softgoal, \text{Realistic simulation}, AND),&\\
A_3 = &(3, Softgoal, \text{Simple design}, AND),&\\
A_4 = &(4, Softgoal, \text{Easy to use}, AND),&\\
A_5 = &(5, Goal, \text{Generate traffic}, AND),&\\
A'_5 = &(5, Goal, \text{Generate traffic}, XOR),&\\
A_6 = &(6, Task, \text{Wrap cars}, AND),&\\
A'_6 = &(6, Task, \text{Create new cars}, AND),&\\
A_7 = &(7, Task, \text{Keep same cars}, AND),&\\
A_8 = &(8, Dep, 4, 1),&\\
A_9 = &(9, PosContr, 6, 2),&\\
A_{10} = &(10, NegContr, 6, 3),&\\
A_{11} = &(11, Decomp, 6, 5),&\\
A_{12} = &(12, Decomp, 7, 5),&\\
A_{13} = &(13, GenArg, \text{Redundant}),&\\
A_{14} = &(14, GenArg, \text{Necessary}),&\\
A_{15} = &(15, GenArg, \text{No effect}),&\\
A_{16} = &(16, GenArg, \text{Changes traffic flow}),&\\
A_{17} = &(ActIE,0,1),\ldots,A_{23}=(ActIE,0,7)&\\
\end{flalign*}
This model is then formalized as $RatGRL=(Arg, Att)$ where:
\begin{flalign*}
Arg = &\{A_0,\ldots,A_5, A'_5,A_6,A'_6,A_7,\ldots,A_{23}\}\\
Att= &\{(A'_{5},A_5), (A'_{6},A_{6}), (A_{13},A_{4}), (A_{14},A_{13}),\\
     & (A_{15},A_{9}),(A_{16},A_{15})\}\\
\end{flalign*}

@@

From Figure~\ref{fig:example-small3}, it can be read from that arguments $A_5$, $A_6$, $A_{13}$ and $A_{15}$ are currently disabled (rejected). However, we did not yet make precise how exactly this is computed. We will do so in the following definitions.
\begin{figure}[b]
\centering
\includegraphics[]{img/Example1-new-arguments.pdf}
\caption{Example argumentation framework, subset of the RationalGRL model from Figure~\ref{fig:example-small3}.}
\label{fig:goalmodeling:arg2}
\end{figure}
In order to compute when an argument is accepted and when not we use argumentation semantics.  We use the standard approach by Dung~\cite{Dung1995}.

@@

The notion of admissible sets gives rise to various possible extensions of an argumentation framework; in this article, we use the preferred extension. In Figure~\ref{fig:goalmodeling:arg2}, there is one preferred extension, namely $\{A_4, A'_5, A_{14}\}$. It is possible to have multiple preferred extensions in cases where the argumentation framework contains cycles. A simple example of such an argumentation framework is shown in Figure~\ref{fig:goalmodeling:arg3}, where arguments $A_x$ and $A_y$ attack each other. There are two preferred extensions, namely $\{A_x\}$ and $\{A_y\}$. Although the algorithms in Section~\ref{sect:algorithms} do not generate mutually attacking arguments such as in Figure~\ref{fig:goalmodeling:arg3}, our formal framework does not explicitly forbid attack cycles in RationalGRL models.

\begin{figure}[b]
\centering
\includegraphics[]{img/example-mutual-attack.pdf}
\caption{Example of a cyclic argumentation framework.}
\label{fig:goalmodeling:arg3}
\end{figure}

@@

Take our two simple examples. In Figure~\ref{fig:goalmodeling:arg2}, we have that arguments $A_4$, $A'_5$ and $A_{14}$ are justified and arguments $A_5$ and $A_{13}$ are rejected. In Figure~\ref{fig:goalmodeling:arg3}, both arguments $A_x$ and $A_y$ are undecided. Returning to our larger example from Figure~\ref{fig:example-small3}, we can see that arguments $A_5$, $A_6$, $A_{13}$ and $A_{15}$ are rejected and all the other arguments are acceptable.

@@

\begin{algorithm}[t]
  \caption{GRL to RationalGRL Translation}
  \label{alg:translation:to-rationalgrl}
  \begin{algorithmic}[1]
    \Procedure{$ToRationalGRL$}{$GRL$}
    \State $Arg \leftarrow IE\cup Act \cup R_{ActIE}\cup Link$\label{alg:translation:to-rationalgrl:args}
    \State $Att \leftarrow \emptyset$\label{alg:translation:to-rationalgrl:att}
    \State \Return $(Arg, Att)$\label{alg:translation:to-rationalgrl:return}
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

As discussed in Section~\ref{sect:overview}, the argument schemes and critical questions of Table~\ref{table:argument-schemes} all lead to one of three operations: \textsf{INTRO}
introduces a new RationalGRL element and \textsf{DISABLE} creates a new argument that attacks another argument. The \textsf{REPLACE} operation is can be seen as a combination of \emph{INTRO} and \emph{DISABLE}: a new argument corresponding to a GRL element is added and this new argument attacks a previous version of the element or link. We will discuss all three operations in separate sections below.

@@

Algorithm~\ref{alg:add-actor} takes one argument, namely the name of the actor $a$. On line~\ref{alg:as0:1} of the algorithm, a new (unique) id is minted as the identifier of the new actor, which is assigned with its corresponding name to the variable $actor$. On line~\ref{alg:as0:2} the actor is added as a new argument. As an example, we can formalize the addition of actor ``Traffic Simulator'' to an empty RationalGRL model (i.e. $Arg=\emptyset$ and $Att=\emptyset$)as executing the algorithm $AS_0$(Traffic simulator), which results in a RationalGRL model with argument $A_0 = (0, Actor, \text{Traffic simulator})\in Arg$.

>>>>

In Section~\ref{sect:overview}, we have shown through a language definition and informal examples from our case study that it is possible to trace elements of the goal model back to their underlying arguments (\textbf{requirement 2}), and that it is possible to determine the effect of changes in the underlying argumentation on the goal model, and vice versa (\textbf{requirement 3}). A formal rendition of this traceability will be presented in this section, in which we present a logical formalization of RationalGRL. This is done for multiple reasons: (i) Most approaches in formal argumentation (cf. Section~\ref{sect:background:pras}) use formal logic, allowing us to employ existing technique directly in order to compute which arguments are accepted and which are rejected, (ii) we can be more precise about how critical questions are answered, (iii) we can show that RationalGRL models can be translated to valid GRL models and visa versa in a precise way, and (iv) the formal approach is a basis for automating the framework in terms of tool support, which we present in the next section.

In Sections \ref{sect:formalframework:grl} and \ref{sect:formalframework:rationalgrl} we formalize a static representation of our framework based on the metamodel (Figure~\ref{fig:metamodel}). We first provide a formal specification of a GRL model in Section~\ref{sect:formalframework:grl}, and we extend this with arguments and attack links in the second subsection, hereby obtaining a formal specification of a RationalGRL model. In Section~\ref{sect:formalframework:translation} we then present algorithms in order to translate a GRL model into a RationalGRL model, and vice versa. Finally, in Section~\ref{sect:algorithms} we turn to the dynamics of our framework, developing algorithms for instantiating argument schemes and answering critical questions and thus formally capturing the \textsf{INTRO}, \textsf{REPLACE} and \textsf{DISABLE} operations of which examples were previously given in Section~\ref{sect:overview:examples}.

@@

\begin{definition}[General definitions]
\label{def:set-definitions}
We define the following sets:
\begin{itemize}
\item $IETypes = \{Softgoal, Goal, Task, Resource\}$,
\item $LinkTypes = \{PosContr, NegContr, Dep, Decomp\}$\footnote{Recall from Section~\ref{sect:background} that for contribution links we only distinguish between positive and negative contributions. Extending the formalization model to include all the GRL values is straightforward but has been omitted here for conciseness.},
\item $Types = IETypes \cup LinkTypes\cup\{Actor, ActIE, GenArg\}$,
\item $Names$ is a finite set of strings,
\item $DecompTypes = \{AND,OR,XOR\}$.
\end{itemize}
\end{definition}
Next, we define an intentional element.

\begin{definition}[Intentional Element]
\label{def:ie}
An intentional element is a tuple $ie = (id, type, name, decomptype)$, where:
\begin{itemize}
\item $id\in \mathbb{N}$ is a unique identifier for the element,
\item $type\in IETypes$ specifies the type of the element,
\item $name \in Names$ is a string description of the element,
\item $decomptype\in DecompTypes$ refers to the type of decomposition.\footnote{Note that, like in the metamodel, the decomposition type is defined on the element.}
\end{itemize}
A set of intentional elements is denoted by $IE$.
\end{definition}

@@

\begin{definition}[Actor]
\label{def:actor}
An actor is a tuple $act=(id,type, name)$, where:
\begin{itemize}
\item $id\in\mathbb{N}$ is the identifier of the actor, 
\item $type = Actor$ states that this tuple is an actor.
\item $name\in Names$ is a string description of its name.
\end{itemize}
A set of actors is denoted by $Act$.
\end{definition}
We can formalize the actor in our example (Figure~\ref{fig:example-small}) as $(0,Actor,\text{Traffic Simulator})$.%, and we can for instance state $act_0.name = \text{Traffic Simulator}$.

@@

Note that Actor-IE relations do not have an $id$: they are themselves not elements of a GRL model but rather indicate relations between elements of a GRL model (i.e., intentional elements and actors). The relation between the \emph{Traffic Simulator} actor ($id = 0$) and the \emph{Car objects} resource ($id=1$), for example, can be formalized as $(ActIE, 0, 1)$.

@@

@@

Definition \ref{def:grl-model} only sums up the elements of the model and not the constraints that make a \emph{valid} GRL model. We will do so in the next definition. Note that in this definition, we use a subscript notation to refer to an element with a specific id. That is, $IE_i, Link_j$, and $Act_k$ refer respectively to the IE with id $i$, the link with id $j$, and the actor with id $k$.

\begin{definition}[Valid GRL Model]
\label{def:valid-grl-model}
A GRL model $GRL=(IE, Act, R_{ActIE}, Link)$ (Def.~\ref{def:grl-model}) is a \emph{valid GRL model} iff the following conditions are satisfied:
\begin{enumerate}
\item ids are globally unique across IEs, Links, and Actors, i.e., let $X,Y\in \{IE,Act, Link\}$. For all $X_i$ and $Y_j$: if $i=j$ then $X=Y$ and $X_i=Y_j$.
\item Intentional elements of actors exist: $\forall (ActIE, i,j)\in R_{ActIE}: \exists act_i \in Act \wedge \exists ie_j \in IE$.
\item An intentional element belongs at most to one actor: $\forall ie_i\in IE: |\{(ActIE,j,i)\in R_{ActIE}\}| \le 1$.
\item Links connect intentional elements: $\forall (i,type, j,k)\in Link: \{ie_j,ie_k\}\subseteq IE$.
\end{enumerate}
\end{definition}

Let us briefly verify that our previous formalization of Figure~\ref{fig:example-small} satisfies all the constraints of Definition~\ref{def:valid-grl-model}:
\begin{enumerate}
\item All elements in the formalization have different ids, so this constraint is satisfied.
\item $R_{ActIE}$ contains one element for each IE with id $i$, so this constraint is satisfied as well. Note that, in line with the GRL metamodel, $R_{ActIE}$ does not relate links with actors. 
\item There is one actor ($id=0$) and this is the only actor that appears in $R_{ActIE}$ so this constraint is satisfied.
\item All links connect IEs: the contribution links connect elements with ids 2, 3, and 6, which are all IEs; the decomposition links connect elements with ids 5, 6, and 7, which are all IEs; and the dependency link connects id 1 with 4, which are both IEs.
\end{enumerate}

@@

\begin{definition}[Argument]
\label{def:argument}
An argument $A$ is on of the following tuples:
\begin{itemize}
\item An intentional element $ie$ (Def.~\ref{def:ie}), 
\item An actor $act$ (Def.~\ref{def:actor}),
\item An Actor-IE relation $r_{ActIE}$ (Def.~\ref{def:act-ie-relation}), 
\item A link $link$ (Def.~\ref{def:link}),
\item A generic argument $ga$ (Def.~\ref{def:generic-argument}).
\end{itemize}
\end{definition}

@@

\begin{definition}[Attack Link]
\label{def:link:attack}
Given a set of arguments $Arg$, an attack link $att=(A_i,A_j)$ means:
\begin{itemize}
\item $A_i\in Arg$ is the argument performing that attack,
\item $A_j\in Arg$ is the argument being attacked.
\end{itemize}
A set of attack links is denoted by $Att$.
\end{definition}

As an example, take the arguments $A_5$ for the goal `Generate traffic' ($AND$ decomposition), $A'_5$ for the goal `Generate traffic' ($XOR$ decomposition), $A_4$ for the softgoal `Easy to use' and the generic argument $A_{13}$ (`Redundant') against the softgoal (`Easy to use'). Given these arguments there are two attack links (Figure~\ref{fig:example-small3}), namely $(A'_{5},A_{5})$ and $(A_{13}, A_{4})$.

We now define a RationalGRL model.

@@

\begin{flalign*}
A_0 = &(0, Actor, \text{Traffic simulator})&\\
A_1 = &(1, Task, \text{Car objects}, AND),&\\
A_2 = &(2, Softgoal, \text{Realistic simulation}, AND),&\\
A_3 = &(3, Softgoal, \text{Simple design}, AND),&\\
A_4 = &(4, Softgoal, \text{Easy to use}, AND),&\\
A_5 = &(5, Goal, \text{Generate traffic}, AND),&\\
A'_5 = &(5, Goal, \text{Generate traffic}, XOR),&\\
A_6 = &(6, Task, \text{Create new cars}, AND),&\\
A_7 = &(7, Task, \text{Wrap cars}, AND),&\\
A'_7 = &(7, Task, \text{Keep same cars}, AND),&\\
A_8 = &(8, Dep, 4, 1),&\\
A_9 = &(9, PosContr, 6, 2),&\\
A_{10} = &(10, NegContr, 6, 3),&\\
A_{11} = &(11, Decomp, 6, 5),&\\
A_{12} = &(12, Decomp, 7, 5),&\\
A_{13} = &(13, GenArg, \text{Redundant}),&\\
A_{14} = &(14, GenArg, \text{Necessary}),&\\
A_{15} = &(15, GenArg, \text{No effect}),&\\
A_{16} = &(16, GenArg, \text{Changes traffic flow}),&\\
A_{17} = &(ActIE,0,1),\ldots,A_{23}=(ActIE,0,7)&\\
\end{flalign*}
This model is then formalized as $RatGRL=(Arg, Att)$ where:
\begin{flalign*}
Arg = &\{A_0,\ldots,A_5, A'_5,A_6,A_7,A'_7\ldots,A_{23}\}\\
Att= &\{(A'_{5},A_5), (A'_{7},A_{7}), (A_{13},A_{4}), (A_{14},A_{13}),\\
     & (A_{15},A_{9}),(A_{16},A_{15})\}\\
\end{flalign*}

@@

From Figure~\ref{fig:example-small3}, it can be read from that arguments $A_5$, $A_7$, $A_{13}$ and $A_{15}$ are currently disabled (rejected). However, we did not yet make precise how exactly this is computed. We will do so in the following definitions.
\begin{figure}[b]
\centering
\includegraphics[]{img/Example1-new-arguments.pdf}
\caption{Example argumentation framework, subset of the RationalGRL model from Figure~\ref{fig:example-small3}.}
\label{fig:goalmodeling:arg2}
\end{figure}
In order to compute when an argument is accepted and when not we use argumentation semantics.  We use the standard approach by Dung~\cite{Dung1995}.

@@

The notion of admissible sets gives rise to various possible extensions of an argumentation framework; in this article, we use the preferred extension. In Figure~\ref{fig:goalmodeling:arg2}, there is one preferred extension, namely $\{A_4, A'_5, A_{14}\}$. It is possible to have multiple preferred extensions in cases where the argumentation framework contains cycles. A simple example of such an argumentation framework is shown in Figure~\ref{fig:goalmodeling:arg3}, where arguments $A_x$ and $A_y$ attack each other. There are two preferred extensions, namely $\{A_x\}$ and $\{A_y\}$. Although the algorithms in Section~\ref{sect:algorithms} do not generate mutually attacking arguments such as in Figure~\ref{fig:goalmodeling:arg3}, our formal framework does not explicitly forbid attack cycles in RationalGRL models. We discuss this in more detail in Section~\ref{sect:discussion:futurework}.

\begin{figure}[ht]
\centering
\includegraphics[]{img/example-mutual-attack.pdf}
\caption{Example of a cyclic argumentation framework.}
\label{fig:goalmodeling:arg3}
\end{figure}

@@

Take our two simple examples. In Figure~\ref{fig:goalmodeling:arg2}, we have that arguments $A_4$, $A'_5$ and $A_{14}$ are acceptable and arguments $A_5$ and $A_{13}$ are rejected. In Figure~\ref{fig:goalmodeling:arg3}, both arguments $A_x$ and $A_y$ are undecided. Returning to our larger example from Figure~\ref{fig:example-small3}, we can see that arguments $A_5$, $A_7$, $A_{13}$ and $A_{15}$ are rejected and all the other arguments are acceptable.

@@

\begin{algorithm}[ht]
  \caption{GRL to RationalGRL Translation}
  \label{alg:translation:to-rationalgrl}
  \begin{algorithmic}[1]
    \Procedure{$ToRationalGRL$}{$GRL$}
    \State $Arg \leftarrow IE\cup Act \cup R_{ActIE}\cup Link$\label{alg:translation:to-rationalgrl:args}
    \State $Att \leftarrow \emptyset$\label{alg:translation:to-rationalgrl:att}
    \State \Return $(Arg, Att)$\label{alg:translation:to-rationalgrl:return}
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

As discussed in Section~\ref{sect:overview}, the argument schemes and critical questions of Table~\ref{table:argument-schemes} all lead to one of three operations: \textsf{INTRO}
introduces a new RationalGRL element and \textsf{DISABLE} creates a new argument that attacks another argument. The \textsf{REPLACE} operation is can be seen as a combination of \textsf{INTRO} and \textsf{DISABLE}: a new argument corresponding to a GRL element is added and this new argument attacks a previous version of the element or link. We will discuss all three operations in separate sections below.

@@

Algorithm~\ref{alg:add-actor} takes one argument, namely the name of the actor $a$. On line~\ref{alg:as0:1} of the algorithm, a new (unique) id is minted as the identifier of the new actor, which is assigned with its corresponding name to the variable $actor$. On line~\ref{alg:as0:2} the actor is added as a new argument. As an example, we can formalize the addition of actor ``Traffic Simulator'' to an empty RationalGRL model (i.e. $Arg=\emptyset$ and $Att=\emptyset$) as executing the algorithm $AS_0$(Traffic simulator), which results in a RationalGRL model with argument $A_0 = (0, Actor, \text{Traffic simulator})\in Arg$.
